---
title: "R Notebook"
output:
  word_document: default
  pdf_document:
    latex_engine: xelatex
  html_notebook: default
always_allow_html: yes
---

```{r setup, include=FALSE}

# This chunk shows/hides the code in your final report. When echo = TRUE, the code
# is shown in the report. When echo = FALSE, the code is hidden from the final report.
# We would like to see your code, so please leave the setting as is during the course.
# This chunk will not show up in your reports, so you can safely ignore its existence.

knitr::opts_chunk$set(echo = TRUE)

```


The following is your first chunk to start with. Remember, you can add chunks using the menu
above (Insert -> R) or using the keyboard shortcut Ctrl+Alt+I. A good practice is to use
different code chunks to answer different questions. You can delete this comment if you like.

Other useful keyboard shortcuts include Alt- for the assignment operator, and Ctrl+Shift+M
for the pipe operator. You can delete these reminders if you don't want them in your report.


```{r}
#setwd("C:/") #Don't forget to set your working directory before you start!

library("tidyverse")
library("tidymodels")
library("plotly")
library("skimr")
```

```{r}
library("lubridate")
library("car")
```


```{r}

dfw <-read_csv("walmartSales.csv")
```
```{r}
summary(dfw)
skim(dfw)
```


```{r}
#1
fitCPI<- lm(formula=Weekly_Sales~CPI,data=dfw)
summary(fitCPI)
```


```{r}
#2
plot<- dfw %>% 
  filter(Store==10) %>% 
  ggplot(aes(x=CPI,y=Weekly_Sales))+
  geom_point()+
  geom_smooth(method=lm)

plot
ggplotly(plot)
```
```{r}
plot<- dfw %>% 
  filter(Store==11) %>% 
  ggplot(aes(x=CPI,y=Weekly_Sales))+
  geom_point()+
  geom_smooth(method=lm)

plot
ggplotly(plot)
```


```{r}
plot<- dfw %>% 
  filter(Store==12) %>% 
  ggplot(aes(x=CPI,y=Weekly_Sales))+
  geom_point()+
  geom_smooth(method=lm)

plot
ggplotly(plot)
```

```{r}
# 2 store 13
plot<- dfw %>% 
  filter(Store==13) %>% 
  ggplot(aes(x=CPI,y=Weekly_Sales))+
  geom_point()+
  geom_smooth(method=lm)

plot
ggplotly(plot)
```

```{r}
#3
plot<- dfw %>% 
  filter(year(Date)==2012) %>% 
  ggplot(aes(x=CPI,y=Weekly_Sales))+
  geom_point()+
  geom_smooth(method=lm)

plot
ggplotly(plot)
```


```{r}
#4
plot<- dfw %>% 
  filter(year(Date)==2010,Store==1) %>% 
  ggplot(aes(x=CPI,y=Weekly_Sales))+
  geom_point()+
  geom_smooth(method=lm)

plot
ggplotly(plot)
```



```{r}
#5
fitCPISize<- lm(formula=Weekly_Sales~CPI+Size,data=dfw)
summary(fitCPISize)
```
```{r}
anova(fitCPI, fitCPISize)
```

```{r}
#7
fitFull<- lm(formula=Weekly_Sales~.-Store-Date,data=dfw)
summary(fitFull)
```


```{r}
anova(fitFull, fitCPISize)
```


```{r}
#8
fitFullTemp<- lm(formula=Weekly_Sales~.-Store-Date+I(Temperature^2),data=dfw)
summary(fitFullTemp)
```


```{r}
plot<- dfw %>% 
  ggplot(aes(x=Temperature,y=Weekly_Sales))+
  geom_smooth(method=lm,formula=y~x+I(x^2))

plot
ggplotly(plot)
```


```{r}
#9 a
set.seed(333)
#9b
dfwTrain <- dfw %>% dplyr::sample_frac (0.8)
dfwTest <-dplyr:: setdiff (dfw,dfwTrain)
#9c
fitOrg <-lm(formula=Weekly_Sales~.-Store-Date+I(Temperature^2),data=dfwTrain)
summary(fitOrg)
```
```{r}
tidy (fitOrg)
```

```{r}
resultsOrg <- dfwTest %>%
  			mutate(predictedSales = predict(fitOrg, dfwTest))
resultsOrg
```


```{r}
#9e
performance <- metric_set(rmse, mae)
performance(resultsOrg,truth=Weekly_Sales,estimate=predictedSales)
```


```{r}
#9f
fitOrgDate <-lm(formula=Weekly_Sales~.-Store+I(Temperature^2),data=dfwTrain)
summary(fitOrgDate)
```


```{r}
tidy(fitOrgDate)
```
```{r}
resultsOrgDate <- dfwTest %>%
  			mutate(predictedSales = predict(fitOrgDate, dfwTest))
resultsOrg


```


```{r}
performance <- metric_set(rmse, mae)
performance(resultsOrgDate,truth=Weekly_Sales,estimate=predictedSales)
```

```{r}
anova(fitOrg,fitOrgDate)
```

```{r}
#9g
fitOrgNoUn <-lm(formula=Weekly_Sales~.-Store-Date-Unemployment+I(Temperature^2),data=dfwTrain)
summary(fitOrgNoUn)
tidy(fitOrgNoUn)
resultsOrgNoUn <- dfwTest %>%
  			mutate(predictedSales = predict(fitOrgNoUn, dfwTest))
resultsOrgNoUn
performance(resultsOrgNoUn,truth=Weekly_Sales,estimate=predictedSales)
```


```{r}
#10

dfw

```


```{r}
set.seed(333)
fitLog <-lm(formula=log1p(Weekly_Sales)~.-Store-Date+I(Temperature^2),data=dfwTrain)
summary(fitLog)
tidy(fitLog)
resultsLog <- dfwTest %>%
  			mutate(predictedLogSales = exp(predict(fitLog, dfwTest)))

resultsLog
performance(resultsLog,truth=Weekly_Sales,estimate=predictedLogSales)
```

```{r}

plot(fitLog)

```
```{r}
plot(fitOrg)
```


```{r}
#autocorrelation
dfw %>% 
  modelr::add_residuals(fitOrg,var="resid") %>% 
  ggplot(aes(Date,resid))+
  geom_line()

dfw %>% 
  modelr::add_residuals(fitLog,var="resid") %>% 
  ggplot(aes(Date,resid))+
  geom_line()
```


```{r}
#multicollinearity
library(car)
car::vif(fitOrg)
car::vif(fitLog)
```


```{r}
#bonus
dfwnew <- dfw %>% 
  mutate(sales_sq_ft=Weekly_Sales/Size)
dfwnew
```


```{r}
set.seed(333)
dfwNewTrain <- dfwnew %>% dplyr::sample_frac (0.8)
dfwNewTest <-dplyr:: setdiff (dfwnew,dfwNewTrain)
fitSalesSqFoot <- lm(formula=sales_sq_ft~.-Store-Date-Weekly_Sales+I(Temperature^2),data=dfwNewTrain)
summary(fitSalesSqFoot)
tidy(fitSalesSqFoot)
```


```{r}

resultsSq <- dfwNewTest %>%
  			mutate(predictedSqSales = predict(fitSalesSqFoot, dfwNewTest))
resultsSq
performance(resultsSq,truth=sales_sq_ft,estimate=predictedSqSales)
```

```{r}
#removing size variable
fitSalesSqFoot <- lm(formula=sales_sq_ft~.-Store-Date-Size-Weekly_Sales+I(Temperature^2),data=dfwNewTrain)
summary(fitSalesSqFoot)
tidy(fitSalesSqFoot)

resultsSq <- dfwNewTest %>%
  			mutate(predictedSqSales = predict(fitSalesSqFoot, dfwNewTest))
resultsSq
performance(resultsSq,truth=sales_sq_ft,estimate=predictedSqSales)
```


